---
title: "Project 4"
author: "Jordan Leung, Jingkai Li, Henrique Saboya, Yijia Li"
date: "11/29/2017"
output:
  html_document: default
  pdf_document: default
---

## Step 0: Load the packages, specify directories and commands

```{r}
#if (!require("pacman")) install.packages("pacman")
#pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)

```

Commands:

```{r}
#Read raw data files
read.movie.data = F
read.ms.data = F

#Reshape data to wide format
reshape.movie = F
reshape.ms = F

#Load Rdata
load.movie.data = T
load.ms.data = T

#Implementation algorythims
model.clustering = T
cross.validate.model.clustering = F
model.sim.rank <- T
```

## Step 1: Load and process the data

Read Movie Dataset:

```{r}
if (read.movie.data){

  #Read dataset from directory
  movie.data.train <- read.csv("../data/movie_data_train.csv")
  movie.data.test <- read.csv("../data/movie_data_test.csv")
  
  movie.data.train <- movie.data.train[,-1]
  movie.data.test <- movie.data.test[,-1]
  
  #Check dataset information
  paste("Data Dimension:", dim(movie.data.train)[1], "x", dim(movie.data.train)[2])
  paste("Number of Unique Movies:",length(unique(movie.data.train[,2])))
  paste("Number of Unique Users:",length(unique(movie.data.train[,3])))
  paste("Number of 0 ratings:", sum(movie.data.train[,4] == 1))

}
```

Read ms Dataset:

```{r}
if (read.ms.data){

  #Read dataset from directory
  ms.data.train <- read.csv("../data/ms_data_train.csv")
  ms.data.test <- read.csv("../data/ms_data_test.csv")
  
  ms.data.train <- ms.data.train[,-1]
  ms.data.test <- ms.data.test[,-1]
  
  #Reshapes TRAIN dataframe -------------------------------------------
  User <- rep(NA, nrow(ms.data.train))
  
  for(i in 1:nrow(ms.data.train)){
    User[i] <- ifelse(ms.data.train[i,1] == "C", ms.data.train[i,3], User[i-1])
  }
  ms.data.train$User <- User
  ms.data.train <- ms.data.train[ms.data.train$V1 == "V",]
  ms.data.train <- ms.data.train[,-1]
  
  names(ms.data.train) <- c("Vroot", "Visits", "User")
  
  #Reshapes TEST dataframe -------------------------------------------
  User <- rep(NA, nrow(ms.data.test))
  
  for(i in 1:nrow(ms.data.test)){
    User[i] <- ifelse(ms.data.test[i,1] == "C", ms.data.test[i,3], User[i-1])
  }
  ms.data.test$User <- User
  ms.data.test <- ms.data.test[ms.data.test$V1 == "V",]
  ms.data.test <- ms.data.test[,-1]
  
  names(ms.data.test) <- c("Vroot", "Visits", "User")
  
  #Clean
  rm(User, i)
}
```

Reshape and save movie data:

```{r}
if(reshape.movie){

  #Reshapes dataframe
  movie.data.train <- reshape(movie.data.train, 
                              v.names = "Score", 
                              direction = "wide", 
                              idvar = "User", 
                              timevar = "Movie")
  
   movie.data.test <- reshape(movie.data.test, 
                              v.names = "Score", 
                              direction = "wide", 
                              idvar = "User", 
                              timevar = "Movie") 
  
  
  
  paste("Data Dimension:", dim(movie.data.train)[1], "x", dim(movie.data.train)[2])
  paste("Data Dimension:", dim(movie.data.test)[1], "x", dim(movie.data.test)[2])
  
  #Save files to data directory
  save(movie.data.train, file = "../data/movie_data_train_wide.Rdata")
  save(movie.data.test, file = "../data/movie_data_test_wide.Rdata")
  }
```

Reshape and save ms data:

```{r}
if(reshape.ms){

  #Reshapes dataframe
  ms.data.train <- reshape(ms.data.train, 
                              v.names = "Visits", 
                              direction = "wide", 
                              idvar = "User", 
                              timevar = "Vroot")
  
   ms.data.test <- reshape(ms.data.test, 
                              v.names = "Visits", 
                              direction = "wide", 
                              idvar = "User", 
                              timevar = "Vroot") 
  
  
  
  paste("Data Dimension:", dim(ms.data.train)[1], "x", dim(ms.data.train)[2])
  paste("Data Dimension:", dim(ms.data.test)[1], "x", dim(ms.data.test)[2])
  
  #Save files to data directory
  save(ms.data.train, file = "../data/ms_data_train_wide.Rdata")
  save(ms.data.test, file = "../data/ms_data_test_wide.Rdata")
  }
```


## Step 2: Implementation

Load Data:

```{r}
#Load Rdata files
if(load.movie.data){
  load("../data/movie_data_train_wide.Rdata")
  load("../data/movie_data_test_wide.Rdata")
}

if(load.ms.data){
  load("../data/ms_data_train_wide.Rdata")
  load("../data/ms_data_test_wide.Rdata")
}
```

Implement Clustering Model:

```{r}
#Training function
cluster.model.train <- function(data.set, C = 3, replace.na = T, tau = 0.1, max.iter = 12){
  
    #Debbuging-------
    #C = 3
    #data.set = ms.data.train
    #replace.na = T
    #tau = 0.1
    #max.iter = 20
  
    #Set-Up------------------------------------------------
    if(replace.na){
      data.set[is.na(data.set)] <- 0
    }
  
    user <- data.set[,1]
    data.set <- data.set[,-1]
    
    websites <- names(data.set)
    k <- sort(unique(unlist(c(data.set[,-1]))))
    N <- nrow(data.set)
    
    #Step 1------------------------------------------------
    u <- runif(C)
    mu <- u/sum(u)
    
    lambda <- array(NA, dim = c(length(k), ncol(data.set), C))
    
    for(ce in 1:C){
      u <- runif(ncol(data.set))
      u2 <- 1 - u
      
      lambda[1,,ce] <- u
      lambda[2,,ce] <- u2
    }
    
    rm(u, u2)
    
    pi <- matrix(NA, nrow = N, ncol = C)
    pi.old <- matrix(0, nrow = N, ncol = C)
    phi <- matrix(NA, nrow = N, ncol = C)
    D <- matrix(NA, nrow = N, ncol = (length(k)))
    iteration <- 1
    d <- Inf
    #------------------------------------------------------
    
  while(d[length(d)] > tau & iteration < max.iter){
      
    #Step 2------------------------------------------------
    
    for(i in 1:N){
      
      aux <- rep(0, C)
      
      for(j in 1:ncol(data.set)) {
        
        aux <- aux + log(lambda[ data.set[i,j] + 1, j, ]) 
      }
      
      phi[i, ] <- exp(aux)
    }
    
    num <- mu * phi
    den <- apply(num, 1, sum)   
  
    pi <- num/den
    #------------------------------------------------------
    
    #Step 3------------------------------------------------
    
    mu <- apply(pi, 2, sum)/N
    
    for(ce in 1:C){
    
      for(j in 1:ncol(data.set)){
        
      l <- t(pi[, ce]) %*% ifelse(data.set[, j] == 1, 1, 0)
        
      lambda[2, j, ce] <- l/sum(pi[ ,ce])
      lambda[1, j, ce] <- 1 - lambda[2, j, ce] 
        
      }
    }
    
    d <- c(d, norm(pi - pi.old))
    
    pi.old <- pi
    
    iteration <- iteration + 1
    
    print(paste("Iteration:", iteration, "norm d:", d[length(d)]))
  }
    
  return(list("pi" = pi, "lambda" = lambda, "mu" = mu, "iterations" = iteration, 
              "progression" = d, "websites" = websites, "user_list" = user))
}  

#Testing function
cluster.model.test <- function(data.set.test, lambda, mu, pi, websites, replace.na = T, alpha = 5){
  
  #Debugging
  #data.set.test <- ms.data.test
  
  #SetUp-----------------------------------------------------------------
  if(replace.na){
    data.set.test[is.na(data.set.test)] <- 0
  }
  
  user <- data.set.test[,1]
  data.set.test <- data.set.test[,-1]
    
  websites.test <- names(data.set.test)
  websites.test.index <- match(websites.test, websites)
  
  N <- nrow(data.set.test)
  predictions <- as.data.frame(matrix(NA, nrow = N, ncol = ncol(data.set.test)))
  names(predictions) <- websites.test
  #-----------------------------------------------------------------------
  
  #Assign users to cluster and make prediction------------------------------------------------
    
  user.cluster <- apply(pi, 1, which.max)
  
  for(i in 1:N){
    for(j in 1:ncol(predictions)){
      
      cluster <- user.cluster[i]
      index <- websites.test.index[j]
      predictions[i,j] <- as.numeric(which.max(lambda[, index, cluster]) - 1)    

    }
  }
  
  #------------------------------------------------------
  
  #Rank scoring------------------------------------------
  
  d <- 0 #Neutral vote
  C <- c(dim(lambda)[3])
  
  lambda.minor <- lambda[, websites.test.index,]
  recommendations <- matrix(NA, nrow = C, ncol = alpha)
  votes <- matrix(NA, nrow = C, ncol = alpha)
  
  for(ce in 1:C){
    recommendations[ce,] <- order(lambda.minor[,,ce][2,], decreasing = T)[1:alpha]
    a <- recommendations[ce,]
    votes[ce,] <- (lambda.minor[,,ce][2,])[a]
  }
  rm(a)
  
  votes[votes >= 0.5] <- 1
  votes[votes < 0.5] <- 0
  
  ra <- matrix(NA, nrow = nrow(predictions), ncol = 2)
  names(ra) <- c("Ra", "Ra.max")
  
  for(i in 1:nrow(predictions)){
    
    cluster <- user.cluster[i] 
    jay <- 1:alpha
    ra[i,1] <- sum(apply(data.set.test[i, recommendations[cluster,]], 2, max, 0)/(2^((jay-1)/(alpha-1))))  
    
    a <- min(sum(data.set.test[i,]), alpha)
    jay2 <- 1:a
    ra[i,2] <- sum(rep(1, a)/(2^((jay2-1)/(alpha-1))))
  }
  
  R <- round(100 * sum(ra[,1])/sum(ra[,2]), 2)
  print(paste("Rank score:", R))
  #------------------------------------------------------
  
  return(list("predictions" = predictions, "R" = R))
}

```

Implement SimRank model:

Helper functions for SimRank Model
```{r}
# returns the corresponding row or column for a user or movie.
get_movies_num <- function(user){
  u_i <- match(user, users)
  return(graph[u_i,-1])
}

get_users_num <- function(movie){
  m_j <- match(movie, movies)
  return(graph[,m_j+1])
}

# return the users or movies with a non zero
get_movies <- function(user){
  series = get_movies_num(user)
  return(movies[which(series!=0)])
}

get_users <- function(movie){
  series = get_users_num(movie)
  return(users[which(series!=0)])
}

user_simrank <- function(u1, u2, C) {
  if (u1 == u2){
    return(1)
  } else {
  pre = C / (sum(get_movies_num(u1)) * sum(get_movies_num(u2)))
  post = 0
  for (m_i in get_movies(u1)){
    for (m_j in get_movies(u2)){
      i <- match(m_i, movies)
      j <- match(m_j, movies)
      post <- post + movie_sim[i, j]
    }
  }
  return(pre*post)
  }
}

movie_simrank <- function(m1, m2, C) {
  if (m1 == m2){
    return(1)
  } else {
    pre = C / (sum(get_users_num(m1)) * sum(get_users_num(m2)))
    post = 0
    for (u_i in get_users(m1)){
      for (u_j in get_users(m2)){
        i <- match(u_i, users)
        j <- match(u_j, users)
        post <- post + user_sim[i, j]
      }
    }
    return(pre*post)
  }
}

simrank <- function(C=0.8, times = 1, calc_user = T, calc_movie = F, data){
  
  for (run in 1:times){
    
    if(calc_user){
    for (ui in users){
      for (uj in users){
        i = match(ui, users)
        j = match(uj, users)
        user_sim[i, j] <<- user_simrank(ui, uj, C)
      }
    }
    }
    if(calc_movie){
    for (mi in movies){
      for (mj in movies){
        i = match(mi, movies)
        j = match(mj, movies)
        movie_sim[i, j] <<- movie_simrank(mi, mj, C)
      }
    }
    }
  }
}
```

```{r}
if(model.sim.rank){
  graph <- movie.data.train[1:1000, 1:1000]

graph[is.na(graph)] <- 0

graph[,-1][graph[,-1] < 5] <- 0
graph[,-1][graph[,-1] >= 5] <- 1


# set similarity matrices to be calculated
calc_user = T
calc_movie = F

# initialize the similarity matrices
user_sim <- diag(dim(graph)[1])
movie_sim <- diag(dim(graph)[2])

# create list of users and movies
users <- graph[,1]
movies <- colnames(graph[,-1])

simrank(0.8, 1)

colnames(user_sim) <- users
user_sim <- cbind(users, user_sim)
write.csv(user_sim, file='../output/usersim.csv', row.names = FALSE)
}
```

Implement Vector Similarity model:
```{r}
mycosine <- function(x,y){
  c <- sum(x*y) / (sqrt(sum(x*x)) * sqrt(sum(y*y)))
  return(c)
}

cosinesim <- function(x) {
  # initialize similarity matrix
  m <- matrix(NA, nrow=ncol(x),ncol=ncol(x),dimnames=list(colnames(x),colnames(x)))
  cos <- as.data.frame(m)
  
  for(i in 1:ncol(x)) {
    for(j in i:ncol(x)) {
      co_rate_1 <- x[which(x[,i] & x[,j]),i]
      co_rate_2 <- x[which(x[,i] & x[,j]),j]  
      cos[i,j]= mycosine(co_rate_1,co_rate_2)
      cos[j,i]=cos[i,j]        
    }
  }
  return(cos)
}
```

```{r}
matrix3<-movie.data.train
rownames(matrix3)<-movie.data.train$User
matrix3$User<-c()
matrix3<-matrix3[1:1000,]

cosine.user.matrix <- cosinesim(t(matrix3))
userid<-rownames(cosine.user.matrix)
new.matrix<-cbind(userid,cosine.user.matrix)
write.csv(new.matrix, file='users_cosine.csv', row.names = FALSE)
```

Implement Selecting Neighbours Methods:

load similarity matrix
```{r}
matrix1<- read.csv("../data/MSDsim_movie.csv")
userid<-matrix1$X[1:1000]
rownames(matrix1)<- matrix1$X
matrix1$X<-c()
matrix1<-matrix1[1:1000,1:1000]
matrix_new<-as.matrix(matrix1)

#userid<-movie.data.train$User[1:50]
#rownames(matrix1)<- movie.data.train$User[1:50]
#matrix1$X<-c()
#colnames(matrix1)<-movie.data.train$User[1:50]
```

correlation_threshold function
```{r}
correlation_threshold <- function(threshold){
  for(i in 1:nrow(matrix_new)) {
    for(j in 1:ncol(matrix_new)) {
      if (is.na(matrix_new[i,j])==FALSE) {
        if(matrix_new[i,j]<=threshold) {
          matrix_new[i,j]<-substring(colnames(matrix_new)[j], 2)
          #matrix_new[i,j]<-colnames(matrix_new)[j]
        } else {
          matrix_new[i,j]<-NA
        }
      }
    }
  }
  return(matrix_new)
}
```

set threshold=1
```{r}
method_1<-correlation_threshold(1)
method_1 <- cbind(userid, method_1)
write.csv(method_1, file='../output/method_1_MSD.csv', row.names = FALSE)
```

load similarity matrix
```{r}
matrix2<- read.csv("../output/usersim.csv")
userid<-matrix2$users
rownames(matrix2)<- matrix2$users
matrix2$users<-c()
matrix_new<-as.matrix(matrix2)
```

best_n_neighbors function
```{r}
best_n_neighbors <- function(n){
  for(i in 1:nrow(matrix_new)) {
      a <- sort(matrix_new[i,],decreasing = TRUE)[n]
    for(j in 1:ncol(matrix_new)) {
       if (is.na(matrix_new[i,j])==FALSE && is.na(a)==FALSE) {
         if(matrix_new[i,j]>=a) {
            matrix_new[i,j]<-substring(colnames(matrix_new)[j], 2)
            #matrix_new[i,j]<-colnames(matrix_new)[j]
         } else{
            matrix_new[i,j]<-NA
         }
       }
    }
  }
  return(matrix_new)
}
```

set n=20
```{r}
method_2<-best_n_neighbors(20)
method_2 <- cbind(userid, method_2)
write.csv(method_2, file='../output/method_2_SR.csv', row.names = FALSE)
```

combined function
```{r}
combined <- function(threshold,n){
  for(i in 1:nrow(matrix_new)) {
    a <- sort(matrix_new[i,],decreasing = TRUE)[n]
    for(j in 1:ncol(matrix_new)) {
      if (is.na(matrix_new[i,j])==FALSE && is.na(a)==FALSE) {
        if(matrix_new[i,j]>=a && matrix_new[i,j]>=threshold) {
          matrix_new[i,j]<-substring(colnames(matrix_new)[j], 2)
          #matrix_new[i,j]<-colnames(matrix_new)[j]
        } else{
          matrix_new[i,j]<-NA
        }
      }
    }
  }
  return(matrix_new)
}
```

set threshold=0.05,n=20
```{r}
method_3<-combined(0.05,20)
method_3 <- cbind(userid, method_3)
write.csv(method_3, file='../output/method_3_SR.csv', row.names = FALSE)
```

# load similarity matrix
```{r}
matrix4<- read.csv("../output/users_cosine.csv")
userid<-matrix4$userid
rownames(matrix4)<- matrix4$userid
matrix4$userid<-c()
matrix_new<-as.matrix(matrix4)
```

# best_n_neighbors function
```{r}
best_n_neighbors <- function(n){
  for(i in 1:nrow(matrix_new)) {
      a <- sort(matrix_new[i,],decreasing = TRUE)[n]
    for(j in 1:ncol(matrix_new)) {
       if (is.na(matrix_new[i,j])==FALSE && is.na(a)==FALSE) {
         if(matrix_new[i,j]>=a) {
            matrix_new[i,j]<-substring(colnames(matrix_new)[j], 2)
            #matrix_new[i,j]<-colnames(matrix_new)[j]
         } else{
            matrix_new[i,j]<-NA
         }
       }
    }
  }
  return(matrix_new)
}
```

# set n=20
```{r}
method_2<-best_n_neighbors(20)
method_2 <- cbind(userid, method_2)
write.csv(method_2, file='../output/method_2_Cosine.csv', row.names = FALSE)
```
## Step 2: Prediction 
# load packages
```{r}
library(Metrics)
library(pROC)
```
# load data
```{r}
load("/Users/lijingkai/Documents/fall2017-project4-grrp3/data/movie_data_train_wide.Rdata")
load("/Users/lijingkai/Documents/fall2017-project4-grrp3/data/movie_data_test_wide.Rdata")

movie.train<-as.matrix(movie.data.train)
rownames(movie.train)<-movie.train[,1]
movie.train<-movie.train[,-1]
colnames(movie.train)<-substring(colnames(movie.train),7,10)

movie.test<-as.matrix(movie.data.test)
rownames(movie.test)<-movie.test[,1]
movie.test<-movie.test[,-1]
colnames(movie.test)<-substring(colnames(movie.test),7,10)

# neighbour matrix
neighbour<-read.csv("method_1_MSD.csv")
rownames(neighbour)<-neighbour[,1]
colnames(neighbour)<-colnames(neighbour)
neighbour<-neighbour[,-1]

# similarity matrix
similarity<-read.csv("MSDsim_movie.csv")
similarity<-similarity[,-1]
rownames(similarity)<-rownames(movie.train)
colnames(similarity)<-rownames(movie.train)

# change NA to 0
adjust2<-function(matrix){
  matrix[is.na(matrix)]<-0
  return(matrix)
}
```

```{r}
# calculate user average rate
mean.rate<-rowMeans(movie.train[,-1],na.rm = TRUE)

# calculate user rate's variance
var.cal<-function(matrix){
  var<-var(matrix,na.rm=TRUE)
  return(var)
}
var.rate<-apply(movie.train[,-1],1,var.cal)

# extract neighbour of a
neighbour_a<-function(a){
  a.neighbour<-neighbour[rownames(neighbour)==a,]
  a.neighbour<-a.neighbour[is.na(a.neighbour)==FALSE]
  return(a.neighbour)
}

# Extract position of neighbour of a
position<-function(neighboura){
  position_a<-match(neighboura,rownames(similarity))
  return(position_a)
}
```
# deviation from mean
```{r}
meanpredict<-function(a){
  neighboura<-neighbour_a(a)
  n<-length(neighboura)
  pos<-position(neighboura)
  mean.a<-mean.rate[rownames(movie.train)==a]
  mean.u<-mean.rate[pos]
  if(all(is.na(neighboura))==TRUE){
    return(rep(mean.a,ncol(movie.train)))
  } else {
    diff.u<-movie.train[pos,]-matrix(rep(mean.u,ncol(movie.train)),ncol=ncol(movie.train))
    diff.u<-sapply(diff.u,as.numeric)
    diff.u<-matrix(diff.u,ncol=ncol(movie.train))
    diff.u<-adjust2(diff.u)
    
    weight.au<-similarity[rownames(similarity)==a,pos]
    weight.au<-as.numeric(weight.au)
    weight.au<-adjust2(weight.au)
    mul<-as.matrix(t(weight.au)) %*% as.matrix(diff.u)
    
    mean.predict.a<-mean.a+mul/sum(weight.au)
    return(mean.predict.a)
  }
}

mean.predict<-apply(as.matrix(as.numeric(rownames(similarity))),1,meanpredict)
mean.predict<-t(mean.predict)
rownames(mean.predict)<-rownames(movie.train)
colnames(mean.predict)<-colnames(movie.train)
```



# z-scores
```{r}
zpredict<-function(a){
  neighboura<-neighbour_a(a)
  n<-length(neighboura)
  pos<-position(neighboura)
  mean.a<-mean.rate[rownames(movie.train)==a]
  mean.u<-mean.rate[pos]
  var.a<-var.rate[rownames(movie.train)==a]
  var.u<-var.rate[pos]
  
  if(all(is.na(neighboura))==TRUE){
    return(rep(mean.a,ncol(movie.train)))
  } else {
  diff.u<-movie.train[pos,]-matrix(rep(mean.u,ncol(movie.train)),ncol=ncol(movie.train))
  diff.u<-sapply(diff.u,as.numeric)
  diff.u<-matrix(diff.u,ncol=ncol(movie.train))
  diff.u<-adjust2(diff.u)

  weight.au<-similarity[rownames(similarity)==a,pos]
  weight.au<-as.numeric(weight.au)
  weight.au<-adjust2(weight.au)
  
  new.var.u<-matrix(rep(var.u,ncol(movie.train)),ncol=ncol(movie.train))
  new.var.u<-sapply(new.var.u,as.numeric)
  new.var.u<-matrix(new.var.u,ncol=ncol(movie.train))
  
  division<-as.matrix(t(weight.au))%*%as.matrix(diff.u/new.var.u)

  
  z.predict.a<-mean.a+var.a*(division/sum(weight.au))
  return(z.predict.a)
}
}

z.predict<-apply(as.matrix(as.numeric(rownames(similarity))),1,zpredict)
z.predict<-t(z.predict)
rownames(z.predict)<-rownames(movie.train)
colnames(z.predict)<-colnames(movie.train)
```






## Step 3: Evaluation

Test Cluster Model:

```{r}
if(model.clustering){
  best.C <- 4
  
  if(cross.validate.model.clustering){
    r <- c()
    parameters <- c(2,4,6)
    for(par in parameters){
      trained.cluster.model <- cluster.model.train(ms.data.train, C = par)
      
        l <- trained.cluster.model$lambda
        m <- trained.cluster.model$mu
        p <- trained.cluster.model$pi
        w <- trained.cluster.model$websites
       
        testing <- cluster.model.test(ms.data.test, lambda = l, mu = m, pi = p, websites = w, alpha = 7)
        r <- c(r, testing$R)
        print(paste("For number of clusters equal to:", par, "Rank score:", testing$R))
    }
    
    t <- matrix(NA, ncol = length(parameters), nrow = 2)
    t[1,] <- parameters 
    t[2,] <- r
    save(t, file = "../output/cv_cluster_rank_score.Rdata")
    write.csv(t, file = "../output/cv_cluster_rank_score.csv")
    
    print(t)
    best.C <- which.max(r) + 1
    best.C
  }
  

  trained.cluster.model <- cluster.model.train(ms.data.train, C = best.C)
  
  l <- trained.cluster.model$lambda
  m <- trained.cluster.model$mu
  p <- trained.cluster.model$pi
  w <- trained.cluster.model$websites
  
  testing <- cluster.model.test(ms.data.test, lambda = l, mu = m, pi = p, websites = w, alpha = 7)
  
  
  rm(l, m, p, w)
  
  save(trained.cluster.model, file = "../output/trained_cluster_model.Rdata")
}
```
MAE
```{r}
# modify prediction matrix to make it the same order as test data
posit<-match(colnames(movie.test),colnames(mean.predict))
mean.newpredict<-mean.predict[,posit]
z.newpredict<-z.predict[,posit]
# create MAE function
MAE<-function(predict){
  accuracy.mae<-NA
  for (i in 1:nrow(movie.test)){
  position<-which(!is.na(movie.test[i,]))
  prediction<-predict[i,position]
  actual<-movie.test[i,position]
  accuracy.mae[i]<-mae(actual,prediction)
  }
  return(accuracy.mae)
}
# MAE result for both method
mean.mae<-mean(MAE(mean.newpredict))
z.mae<-mean(MAE(z.newpredict))
```
ROC
```{r}
# modify test data
adjust<-function(matrix){
  matrix[matrix<4]<-0
  matrix[matrix>=4]<-1
  return(matrix)
}
test.roc<-adjust(movie.test)
# create ROC function
ROC<-function(predict){
  accuracy.mae<-NA
  for (i in 1:nrow(test.roc)){
    position<-which(!is.na(test.roc[i,]))
    prediction<-predict[i,position]
    actual<-test.roc[i,position]
    accuracy.mae[i]<-auc(actual,predicted=prediction)
  }
  return(accuracy.mae)
}
# ROC result for both method
mean.roc<-mean(ROC(mean.newpredict),na.rm = TRUE)
z.roc<-mean(ROC(z.newpredict),na.rm=TRUE)
```




